---
title: "RBsSECACC5yr"
author: "Saiem Gilani <br><a href='https://twitter.com/saiemgilani' target='blank'><img src='https://img.shields.io/twitter/follow/saiemgilani?color=blue&amp;label=%40saiemgilani&amp;logo=twitter&amp;style=for-the-badge' alt='@saiemgilani'/></a> <a href='https://github.com/saiemgilani' target='blank'><img src='https://img.shields.io/github/followers/saiemgilani?color=eee&amp;logo=Github&amp;style=for-the-badge' alt='@saiemgilani'/></a>"
opengraph:
  image: 
    src: "https://github.com/saiemgilani/recruitR/blob/master/logo.png?raw=true"
  twitter:
    card: summary_large_image
    creator: "@saiemgilani"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{RBsSECACC5yr}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Running Backs Recruiting 2015-2020: SEC & ACC

This is a basic example which shows you how to solve a common problem:

```{r examplerbs,  message=FALSE, warning=FALSE, results='hide'}
if (!requireNamespace('pacman', quietly = TRUE)){
  install.packages('pacman')
}
pacman::p_load_current_gh("saiemgilani/recruitR")

pacman::p_load(tidyverse)
```
Let's say that we are interested in seeing how teams in either the SEC or ACC fared in running back recruiting from 2015-2020. We could gather the information on each conference using the `cfb_recruiting_position` function, like so:
```{r RBs}
sec_positions <- cfbd_recruiting_position(start_year=2015,
                                         end_year = 2020, 
                                         conference = 'SEC')

acc_positions <- cfbd_recruiting_position(start_year=2015,
                                         end_year = 2020, 
                                         conference = 'ACC')

sec_rbs <- sec_positions %>% 
  dplyr::filter(position_group == "Running Back") %>% 
  dplyr::arrange(desc(avg_stars))
acc_rbs <- acc_positions %>% 
  dplyr::filter(position_group == "Running Back") %>% 
  dplyr::arrange(desc(avg_stars))

rbs <- dplyr::bind_rows(sec_rbs,acc_rbs)
print(rbs)

```
## Plotting the Running Backs

You can also create a plot:

```{r plot_rbs}



ggplot(rbs ,aes(x = team, y = commits, fill = avg_stars)) +
  geom_bar(stat = "identity",colour='black') +
  xlab("Team") + ylab("Number of Players") +
  labs(title="2015-2020 Running Back Recruiting - SEC & ACC",
       subtitle="Figure: @SaiemGilani | Data: @CFB_data with #recruitR")+
  geom_text(aes(label = round(avg_stars,2)),color="grey85",
            size = 2.3, position = position_stack(vjust = 0.5))+
  scale_color_gradient2(low = "red",midpoint = 3,mid = "blue",
                        high = "green",space="Lab")+
  facet_wrap(~conference,ncol=2,scales='free')+
  theme(legend.title = element_blank(),
        legend.text = element_text(size = 7, margin=margin(t=0.2,r=3,b=0.2,l=3,unit=c("mm")), 
                                   family = "serif"),
        legend.background = element_rect(fill = "grey99"),
        legend.key.width = unit(.5,"cm"),
        legend.key.size = unit(.5,"cm"),
        legend.position = c(0.3, 0.88),
        legend.margin=margin(t = 0.4,b = 0.4,l=0.1,r=2.7,unit=c('mm')),
        legend.direction = "horizontal",
        legend.box.background = element_rect(colour = "#500f1b"),
        axis.title.x = element_text(size = 12, margin = margin(0,0,1,0,unit=c("mm")), 
                                    family = "serif",face="bold"),
        axis.text.x = element_text(size = 9, margin=margin(0,0,1,0,unit=c("mm")),
                                   face="bold",family = "serif", angle = 45, hjust = 1),
        axis.title.y = element_text(size = 12, margin = margin(0,0,0,0,unit=c("mm")), 
                                    family = "serif",face="bold"),
        axis.text.y = element_text(size = 12, margin = margin(1,1,1,1,unit=c("mm")), 
                                    family = "serif"),
        plot.title = element_text(size = 14, margin = margin(t=0,r=0,b=1.5,l=0,unit=c("mm")),
        lineheight=-0.5, family = "serif",face="bold"),
        plot.subtitle = element_text(size = 12, margin = margin(t=0,r=0,b=2,l=0,unit=c("mm")), 
                                     lineheight=-0.5, family = "serif"),
        plot.caption = element_text(size = 12, margin=margin(t=0,r=0,b=0,l=0,unit=c("mm")),
                                    lineheight=-0.5, family = "serif"),
        strip.text = element_text(size = 10, family = "serif",face="bold"),
        panel.background = element_rect(fill = "grey75"),
        plot.background = element_rect(fill = "grey65"),
        plot.margin=unit(c(top=0.4,right=0.4,bottom=0.4,left=0.4),"cm"))

```
